Near infrared metrology of high performance silicon immersion gratings

### 2015-04-13 chSPIE_2012_CA1/chapter-2012-CA1.tex
include all formatting corrections suggested by R. Penman from his email on April 6, 2015, except for chapter 7 which is still in flux.

\begin{figure}
  \centering
  \subfloat[CA1a photo]{\label{fig:CA1aphoto}\includegraphics[height=5cm]{chSPIE_2012_CA1/figs/ca1_bartest2}}
	~
%  \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[page=1, trim=24cm 15.15cm 2cm 5cm, clip=true, totalheight=0.2\textheight ]{APRA_BOULE_29MM_R3_CA1_X14_2011-03-08}}
   \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[height=4cm]{chSPIE_2012_CA1/figs/ca1a_drawing}}
  \caption[Photo and design drawing of the IGRINS immersion grating]{Photo and design drawing of the immersion grating CA1a in the lab in August 2011.  The entrance face is on the right, with a light green color in the photo (color available in the digital manuscript), which is due to the AR coating.  The grating surface is on the top with microscopic grating lines perpendicular to the long edge of the grating.  In operation a 25 mm circular beam will be incident on the entrance face and will project into an ellipse on the grating surface as seen in the drawing.  The dispersed light will reemerge from the entrance face.  The units in the drawing are mm.  The parent substrate and grating geometry are pictured in Figures 1, 3, and 4 in Wang et al. 2010\cite{2010SPIE.7739E.146W}.  Those figures reveal how the CA1a trapezoid shape and curved rear edge derive from the parent substrate shape.}
  \label{fig:gram}
\end{figure}

@@

%-------------
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=7cm]{chSPIE_2012_CA1/figs/CA1_SEM_cross3}
   \end{tabular}
   \end{center}
   \caption[CA1a SEM]{ \label{fig:CA1aSEM}  Scanning electron micrograph (SEM) of a $\sim$100 $\mu$m cross section of a scrap portion of the immersion grating CA1.  The left panel is the unaltered SEM.  The right panel is a schematic illustrating the grating specifications and the geometry of incident and diffracted beams (thick black line with arrows).  The beam is incident from the left, and diffracts at the facets at the silicon/aluminum interface.  The incident angle $\alpha$ and diffracted beam $\beta$ are measured from the grating normal (shown in blue).  The blaze angle $\delta$ is set by the orientation of the crystal planes with respect to the grating surface.  This angle was designed to be $\delta=71.56^\circ$, which is the angle whose tangent is 3.  The optically active facets are highlighted as short red vertical lines (\emph{color online}).  The regions of the grating above the dashed line do not see the beam.  In the IGRINS design and in our lab testing there is a small out of plane angle $\gamma$ not shown here.  The apparent hillock artifacts on the grating facets are a result of the cross-section preparation process, the measured\cite{2010SPIE.7739E.146W} surface flatness is 1.7 nm.}
   \end{figure} 
%-------------

@@

\begin{figure}
  \centering
\includegraphics[width=0.9\textwidth]{chSPIE_2012_CA1/figs/CA1a_fig_scl2}
  \caption[Optical interferometry of the IGRINS immersion grating]{Optical interferometry of CA1a in reflection off the back surface before cutting and aluminization.  The color scales are in waves of surface error for 632 nm in reflection.  \emph{Left:} Interferogram measured in Littrow reflection at R3 over a 23.75 mm beam on the parent substrate CA1, in the vicinity where CA1a was later cut.  The colorbars show the vertical scale in waves of surface distortion at $\lambda = $ 632.8 nm.  These optical measurements illuminate the back of the grating facets, they were taken before aluminization and should be a good proxy for immersion performance at 2.15 $\mu$m. \emph{Center:} A fit to the large scale surface distortion using the first 200 Zernike polynomials in the Noll Sequence \cite{noll1976}.  \emph{Right:} The residual high spatial frequency surface error constructed from subtracting the fit from the measured surface error.}
  \label{fig:gram}
\end{figure}

@@

\begin{figure}
\begin{center}
 \subfloat[2D Zygo PSF]{\label{fig:zygoPSF2D} \includegraphics[width=0.45\textwidth]{chSPIE_2012_CA1/figs/CA1a_ghost_zygo_2d}}
 \subfloat[1D Log PSF]{\label{fig:logPSF1D} \includegraphics[width=0.45\textwidth]{chSPIE_2012_CA1/figs/CA1a_ghost_1d}}   
  \end{center}
  \caption[Immersion grating interferogram PSF]{\label{fig:PSFzygo}  Left: The 2-dimensional synthetic PSF from interferometric measurements of the air-aluminum reflective interface of CA1a at 632.8 nm at R3.  The dispersion direction is $x$, the cross-dispersion or spatial dimension is $y$.  The units on the axes are in terms of diffraction widths of $\lambda=$ 632.8 nm and $D=$ 25 mm, which were the conditions of the interferometry.  The scale on the 2D image is linear, compare to the intensity levels shown on the right panel.  Right:  The 1D logarithmically scaled horizontal line profile of the PSF of CA1a under three conditions.  The black is the synthetic interferometric PSF.  The red is the lab-measured PSF in reflection at 632 nm with a 20 mm beam.  This measurement is not diffraction limited.  The green line is the measurement at 543 nm in reflection with a 20 mm beam.}
\end{figure}

@@

\begin{figure}
\begin{center}
    \includegraphics[width=1.0\textwidth]{chSPIE_2012_CA1/figs/GTA_cam_model_ref_tilt.jpg}
  \end{center}
  \caption[Schematic of the CROWBAR: Custom Robotic Order, Wavelength, and Blaze Angle Recorder]{\label{fig:GTAview} View of the monochromator, periscope, and swing arm-camera system with the beam path highlighted.  The beam exits the monochromator exit slit (8), where the optical chopper (9) is located.  The beam is collimated by a 1 inch post-slit lens (10).  The periscope system includes 3 mirrors (12, 13a, 13b), only two of which are active at any time.  In the reflective arm of interest to this report, we use mirrors (12) and (13b), with mirror 13a moved clear out of the beam path with a 90$^\circ$ flip mount.  The beam travels about 1 meter (off the image) to an adjustable iris in double pass (14, 16) sandwiching a mirror (15) tilted about 10$^\circ$ from the $z-y$ plane.  The beam travels along the vector terminating on the center of the immersion grating (17).  The immersion grating has its grooves vertical (parallel to the $z-$axis) so that the dispersion occurs in a the $x-y$ plane.  There are typically 3 or 4 orders diffracted $\pm20^\circ$ from the optical axis, for CA1 in our wavelength range of interest ($1.5-2.5 \; \mu$m).  The camera lens (18) and single pixel detector (19) are mounted on a swinging arm which rotates in the $x-y$ plane, with its center of rotation equal to the position of the immersion grating.  The angular range of motion of the swing arm is about +27 to -37$^\circ$ which is set by limit switches and the rigid mechanical structure, which supports the immersion grating and its concomitant fine adjust positioning hardware.  The cartoon arrows demonstrate our angular sign convention which is positive counter clockwise, with zero along the optic axis.  The grating normal is at about -70$^\circ$ with that convention.  The beam path in the monochromator is omitted for clarity.  The lock-in amplifier electronics are marked with number (20).}
\end{figure}

>>>>

\begin{figure}
  \centering
  \subfloat[CA1a photo]{\label{fig:CA1aphoto}\includegraphics[height=4cm]{chSPIE_2012_CA1/figs/ca1_bartest2}}
	~
   \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[height=3.5cm]{chSPIE_2012_CA1/figs/ca1a_drawing}}
  \caption[Photo and design drawing of the IGRINS immersion grating]{Photo and design drawing of the immersion grating CA1a in the lab in August 2011.  The entrance face is on the right, with a light green color in the photo (color available in the digital manuscript), which is due to the AR coating.  The grating surface is on the top with microscopic grating lines perpendicular to the long edge of the grating.  In operation a 25 mm circular beam will be incident on the entrance face and will project into an ellipse on the grating surface as seen in the drawing.  The dispersed light will reemerge from the entrance face.  The units in the drawing are mm.  The parent substrate and grating geometry are pictured in Figures 1, 3, and 4 in Wang et al. 2010\cite{2010SPIE.7739E.146W}.  Those figures reveal how the CA1a trapezoid shape and curved rear edge derive from the parent substrate shape.}
  \label{fig:gram}
\end{figure}

@@

%-------------
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=6cm]{chSPIE_2012_CA1/figs/CA1_SEM_cross3}
   \end{tabular}
   \end{center}
   \caption[CA1a SEM]{ \label{fig:CA1aSEM}  Scanning electron micrograph (SEM) of a $\sim$100 $\mu$m cross section of a scrap portion of the immersion grating CA1.  The left panel is the unaltered SEM.  The right panel is a schematic illustrating the grating specifications and the geometry of incident and diffracted beams (thick black line with arrows).  The beam is incident from the left, and diffracts at the facets at the silicon/aluminum interface.  The incident angle $\alpha$ and diffracted beam $\beta$ are measured from the grating normal (shown in blue).  The blaze angle $\delta$ is set by the orientation of the crystal planes with respect to the grating surface.  This angle was designed to be $\delta=71.56^\circ$, which is the angle whose tangent is 3.  The optically active facets are highlighted as short red vertical lines (\emph{color online}).  The regions of the grating above the dashed line do not see the beam.  In the IGRINS design and in our lab testing there is a small out of plane angle $\gamma$ not shown here.  The apparent hillock artifacts on the grating facets are a result of the cross-section preparation process, the measured\cite{2010SPIE.7739E.146W} surface flatness is 1.7 nm.}
   \end{figure} 
%-------------

@@

\begin{figure}
  \centering
\includegraphics[width=0.95\textwidth]{chSPIE_2012_CA1/figs/CA1a_fig_scl2}
  \caption[Optical interferometry of the IGRINS immersion grating]{Optical interferometry of CA1a in reflection off the back surface before cutting and aluminization.  The color scales are in waves of surface error for 632 nm in reflection.  \emph{Left:} Interferogram measured in Littrow reflection at R3 over a 23.75 mm beam on the parent substrate CA1, in the vicinity where CA1a was later cut.  The colorbars show the vertical scale in waves of surface distortion at $\lambda = $ 632.8 nm.  These optical measurements illuminate the back of the grating facets, they were taken before aluminization and should be a good proxy for immersion performance at 2.15 $\mu$m. \emph{Center:} A fit to the large scale surface distortion using the first 200 Zernike polynomials in the Noll Sequence \cite{noll1976}.  \emph{Right:} The residual high spatial frequency surface error constructed from subtracting the fit from the measured surface error.}
  \label{fig:gram}
\end{figure}

@@

\begin{figure}
\begin{center}
 \subfloat[2D Zygo PSF]{\label{fig:zygoPSF2D} \includegraphics[width=0.48\textwidth]{chSPIE_2012_CA1/figs/CA1a_ghost_zygo_2d}}
 \subfloat[1D Log PSF]{\label{fig:logPSF1D} \includegraphics[width=0.48\textwidth]{chSPIE_2012_CA1/figs/CA1a_ghost_1d}}   
  \end{center}
  \caption[Immersion grating interferogram PSF]{\label{fig:PSFzygo}  Left: The 2-dimensional synthetic PSF from interferometric measurements of the air-aluminum reflective interface of CA1a at 632.8 nm at R3.  The dispersion direction is $x$, the cross-dispersion or spatial dimension is $y$.  The units on the axes are in terms of diffraction widths of $\lambda=$ 632.8 nm and $D=$ 25 mm, which were the conditions of the interferometry.  The scale on the 2D image is linear, compare to the intensity levels shown on the right panel.  Right:  The 1D logarithmically scaled horizontal line profile of the PSF of CA1a under three conditions.  The black is the synthetic interferometric PSF.  The red is the lab-measured PSF in reflection at 632 nm with a 20 mm beam.  This measurement is not diffraction limited.  The green line is the measurement at 543 nm in reflection with a 20 mm beam.}
\end{figure}

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.95\textwidth]{chSPIE_2012_CA1/figs/GTA_cam_model_ref_tilt.jpg}
  \end{center}
  \caption[Schematic of the CROWBAR: Custom Robotic Order, Wavelength, and Blaze Angle Recorder]{\label{fig:GTAview} View of the monochromator, periscope, and swing arm-camera system with the beam path highlighted.  The beam exits the monochromator exit slit (8), where the optical chopper (9) is located.  The beam is collimated by a 1 inch post-slit lens (10).  The periscope system includes 3 mirrors (12, 13a, 13b), only two of which are active at any time.  In the reflective arm of interest to this report, we use mirrors (12) and (13b).  The beam travels about 1 meter (off the image) to an adjustable iris in double pass (14, 16) sandwiching a mirror (15) tilted about 10$^\circ$ from the $z-y$ plane.  The beam travels along the vector terminating on the center of the immersion grating (17).  The immersion grating has its grooves vertical (parallel to the $z-$axis) so that the dispersion occurs in a the $x-y$ plane.  The camera lens (18) and single pixel detector (19) are mounted on a swinging arm which rotates in the $x-y$ plane, with its center of rotation equal to the position of the immersion grating.  The cartoon arrows demonstrate our angular sign convention which is positive counter clockwise, with zero along the optic axis.  The grating normal is at about -70$^\circ$ with that convention.  The lock-in amplifier electronics are marked with number (20).}
\end{figure}
